---
always_allow_html: true
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      comment = "")
```

## R Package for Generalizability Theory

The Gboot package implements bootstrap sampling schemes as described in Tong & Brennan (2004). Two functions, `CalcGTheoryCI` and `CalcGTheoryCINested` produce bootstrapped confidence intervals for crossed and nested designs, respectively. Each function can implement any combination of person, item, and observer (what Tong & Brennan call person, item, rater). 

Within Gboot, you can also simulate data for crossed or nested designs with `sim_dat_2crossed` and `sim_dat_2nested`. 

## Installation

As of now, Gboot is only on GitHub. You can install it with the following:

```{r, eval = FALSE}
remotes::install_github("alanhuebner10/Gboot")
```


## Core Functions and Workflow

Producing bootstrapped confidence intervals for a *p x i* crossed design can be done as follows:

```{r}
library(Gboot)

data("Brennan.3.1")

bootstrappedCI <- CalcGTheoryCI(Data = Brennan.3.1, B = 1000, type = "pi")

summaryCI(bootstrappedCI)

bootViz(bootstrappedCI)
```

Or with simulated data:

```{r}
simData <- sim_dat_2crossed(np = 100, ni = 20, nr = 2,
                            sig_p = 4, sig_i =  2, sig_r = 1,
                            sig_pi = 8, sig_pr = sqrt(2), sig_ir = sqrt(3), 
                            sig_pir = 12)

simulatedBootstrappedCI <- CalcGTheoryCI(Data = simData, B = 1000, type = "pi")

summaryCI(simulatedBootstrappedCI)

bootViz(simulatedBootstrappedCI)
```

